SHARP - II. Mass structure in strong lenses is not necessarily dark matter substructure: A flux ratio anomaly from an edge-on disc

### 2016-02-29 papers/B1555_EdgeOn/Resubmission_v2/B1555_EdgeOn.tex
update for manuscript change

The best-fit model parameters and 68 per cent confidence level (CL) errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:3panel}c. Table \ref{tab:results} also shows the comparison between the observed radio data and the model-predicted image positions and flux ratios. We find that by adding an elongated exponential disc to a smooth SIE model there is significant improvement in the predicted flux ratios when compared to the results for the SIE-only model. 
% with a reduced $\chi^2 = 2.7$
The positions are all in agreement, and the flux ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B. The remaining differences in the fluxes may be due to the real lensed source being slightly extended rather than the point source that we used in our model. The model requires that the \textbf{ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$ but the mass fraction is independent of the lens and source redshifts since the model parameters are scale free).  In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass. Investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc mass fraction within the Einstein radius ranges from 5 to 30 per cent\citep{swells1,swells3,swells6}.} 
%In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.  We therefore interpret the ExpDisc component as a good description of the baryonic mass of the lens galaxy. 
%We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g. from an external shear) that is being partly compensated for by the disc component. Again, more complex mass models require the stronger constraints provided by deep imaging of the full extent of the gravitational arc in future high resolution radio observations.

>>>>

The best-fit model parameters and 68 per cent confidence level (CL) errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:3panel}c. Table \ref{tab:results} also shows the comparison between the observed radio data and the model-predicted image positions and flux ratios. We find that by adding an elongated exponential disc to a smooth SIE model there is significant improvement in the predicted flux ratios when compared to the results for the SIE-only model. 
% with a reduced $\chi^2 = 2.7$
The positions are all in agreement, and the flux ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B. The remaining differences in the fluxes may be due to the real lensed source being slightly extended rather than the point source that we used in our model. The model requires that the \textbf{ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$ but the mass fraction is independent of the lens and source redshifts since this ratio is independent of distance).  In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass. Investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc mass fraction within the Einstein radius ranges from 5 to 30 per cent\citep{swells1,swells3,swells6}.} 
%In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.  We therefore interpret the ExpDisc component as a good description of the baryonic mass of the lens galaxy. 
%We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g. from an external shear) that is being partly compensated for by the disc component. Again, more complex mass models require the stronger constraints provided by deep imaging of the full extent of the gravitational arc in future high resolution radio observations.
